### 2011-10-20 doc/manuscript.tex
Just an update.

%\section*{References}
% The bibtex filename
\bibliographystyle{plos}
\bibliography{siepel-strep}

@@

Figure \ref{fig:tree5}.\ \bf{The species tree of the five genomes inferred using
\texttt{ClonalFrame}.}  SPY is the branch of a clade of \textit{Streptococcus
pyogenes}, SDE is that for \textit{S.\ dysgalactiae} ssp.\textit{\ equisimilis},
and SD is the branch for the three individual genomes of \textit{S.\
dysgalactiae}. The scale is proportional to the expected number of mutations
given the Watterson's estimate of mutation rate and the tree.

Figure \ref{fig:Heatmap-of-recombination}.\ \bf{Heatmap of recombination events 
using the five genomes.}
Each cell of the heat map represents the logarithm base
2 of the number of recombination events inferred relative to its expectation
under the prior, for a donor and recipient pair of branches. The donor is given by
the y-axis; the recipient on the x-axis.  The black colored cells are meaningless
because the recipient species tree branch of the cells are older than the donor
species branch.

Figure \ref{fig:Gene-duplication-loss}.\ \bf{Distribution of inferred gene 
duplication, loss, and transfer events across
the phylogeny.}  Gene counts for
each extant and ancestral species are given at each node of the phylogeny.  For
each branch we denote the number of gains G*, duplications D*, losses L*,
non-recombining transfers T*, and recombinations R*.  The non-recombining
transfer and recombination counts are indicated on the recipient branch (donors
are not indicated).

Figure \ref{fig:h3}.\ \bf{Simulations of the model-based approach for assessing 
the power of recovering recombinant edges.} 
Pairs of species tree branches are shown at x-axis labels.
Three intervals are displayed for each pair. Intervals with solid line with open
circle in the middle are for the logarithm of the fraction to base 2 of the average
number of recombinant edges from the ten simulated recombinant trees 
to the numbers of recombinant edges estimated from Simulation 2. 
Interverals with dotted line are for the logarithm of the fraction to base 2 of
the number of recombinant edges estimated from the real data
to the numbers of recombinant edges estimated from Simulation 2.
Intervals with solid line with closed circle in the middle are for the logarithm
of the fraction to base 2 of the number of recombinant edges estimated from the real data
to the numbers of recombinant edges estimated from Simulation 3. 
The horizontal lines are at the zero.
The intervals range from 5\% quantile to 95\% of quantile.

@@

%=============================================================================
% Table 1. 
\begin{table}
\caption{\label{tab:functional}
\bf{Functional categories asscoiated with 
recombination intensity based on topology-altering recombinant edges.}}
\noindent \begin{centering}
\begin{tabular}{cccl}
\hline 
P-Value & Count & GO term & Description\tabularnewline
\hline 
1.731e-06 & 38 & GO:0009401 & phosphoenolpyruvate-dependent sugar phosphotransferase system\tabularnewline
2.775e-06 & 33 & GO:0008982 & protein-N(PI)-phosphohistidine-sugar phosphotransferase activity\tabularnewline
4.581e-05 & 22 & GO:0006633 & fatty acid biosynthetic process\tabularnewline
0.0001248 & 20 & GO:0008610 & lipid biosynthetic process\tabularnewline
0.0002675 & 45 & GO:0008643 & carbohydrate transport\tabularnewline
0.000513 & 81 & GO:0006412 & translation\tabularnewline
0.0005617 & 13 & GO:0006814 & sodium ion transport\tabularnewline
0.001019 & 40 & GO:0030529 & ribonucleoprotein complex\tabularnewline
0.001203 & 12 & GO:0031402 & sodium ion binding\tabularnewline
0.00206 & 39 & GO:0003735 & structural constituent of ribosome\tabularnewline
0.002115 & 237 & GO:0008152 & metabolic process\tabularnewline
0.00215 & 26 & GO:0019843 & rRNA binding\tabularnewline
0.00287 & 371 & GO:0016740 & transferase activity\tabularnewline
0.003552 & 66 & GO:0005840 & ribosome\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\end{table}
%\clearpage{}
%=============================================================================

%=============================================================================
% Table 2. 
\begin{table}
\caption{\label{tab:go-events}Functional categories asscoiated with 
non-recombining horizontal gene transfer.}
\noindent \begin{centering}
\begin{tabular}{cccl}
\hline 
P-Value & Count & GO term & Description \\
\hline 
7e-61 &  67 & GO:0006313 & transposition, DNA-mediated\\
3e-58 &  59 & GO:0004803 & transposase activity\\
1e-30 &  52 & GO:0015074 & DNA integration\\
1e-28 &  23 & GO:0032196 & transposition\\
1e-13 & 527 & GO:0003677 & DNA binding\\
2e-12 &  86 & GO:0006310 & DNA recombination\\
1e-11 & 197 & GO:0003676 & nucleic acid binding\\
3e-09 &  36 & GO:0016987 & sigma factor activity\\
3e-09 &  36 & GO:0006352 & transcription initiation\\
3e-08 & 142 & GO:0043565 & sequence-specific DNA binding\\
\hline 
\end{tabular}
\par\end{centering}
\end{table}
\clearpage{}
%=============================================================================

%=============================================================================
% Figure 1: Species tree
\begin{figure}
\includegraphics[scale=0.7]{figures/cornellf-3-tree}
\caption{\label{fig:tree5}The species tree of the five genomes inferred using
\texttt{ClonalFrame}.  SPY is the branch of a clade of \textit{Streptococcus
pyogenes}, SDE is that for \textit{S.\ dysgalactiae} ssp.\textit{\ equisimilis},
and SD is the branch for the three individual genomes of \textit{S.\
dysgalactiae}. The scale is proportional to the expected number of mutations
given the Watterson's estimate of mutation rate and the tree.}
\end{figure}
\clearpage{}%
%=============================================================================

%=============================================================================
% Figure 2. Heat map of recombining gene transfer from ClonalOrigin
\begin{figure}
\includegraphics[scale=0.45]{figures/heatmap-recedge}
\caption{\label{fig:Heatmap-of-recombination}
\bf{Heatmap of recombination events using the five genomes.}
Each cell of the heat map represents the logarithm base
2 of the number of recombination events inferred relative to its expectation
under the prior, for a donor and recipient pair of branches. The donor is given by
the y-axis; the recipient on the x-axis.  The black colored cells are meaningless
because the recipient species tree branch of the cells are older than the donor
species branch.}
\end{figure}
\clearpage{}
%=============================================================================

%=============================================================================
% Figure 3. Gene duplication, loss, and transfer
\begin{figure}
\includegraphics[width=6in]{figures/strep-events}
\caption{\label{fig:Gene-duplication-loss} 
\bf{Distribution of inferred gene duplication, loss, and transfer events across
the phylogeny.}  Gene counts for
each extant and ancestral species are given at each node of the phylogeny.  For
each branch we denote the number of gains G*, duplications D*, losses L*,
non-recombining transfers T*, and recombinations R*.  The non-recombining
transfer and recombination counts are indicated on the recipient branch (donors
are not indicated).}
\end{figure}
\clearpage{}%
%=============================================================================

@@

\caption{\label{fig:h3}
\bf{Simulations of the model-based approach for assessing the power of recovering
recombinant edges.} Pairs of species tree branches are shown at x-axis labels.
Three intervals are displayed for each pair. Intervals with solid line with open
circle in the middle are for the logarithm of the fraction to base 2 of the average
number of recombinant edges from the ten simulated recombinant trees 
to the numbers of recombinant edges estimated from Simulation 2. 
Interverals with dotted line are for the logarithm of the fraction to base 2 of
the number of recombinant edges estimated from the real data
to the numbers of recombinant edges estimated from Simulation 2.
Intervals with solid line with closed circle in the middle are for the logarithm
of the fraction to base 2 of the number of recombinant edges estimated from the real data
to the numbers of recombinant edges estimated from Simulation 3. 
The horizontal lines are at the zero.
The intervals range from 5\% quantile to 95\% of quantile.}
\end{figure}
\clearpage{}%
%=============================================================================

@@

%=============================================================================
% Table S2. ClonalFrame Result.
\begin{table}[!ht]
\caption{
\bf{Parameter estimates from \texttt{ClonalFrame}.}
$\theta$ is population mutation rate,
$\delta$ is the average recombinant tract length,
$r/m$ is the relative strength of recombination compared to mutations,
TMRCA is the time to most recent common ancestor, and
$T$ is the total branch length of the inferred species tree.}
\noindent \centering{}\begin{tabular}{cc}
\hline
Parameter & Estimates (95\% credibility interval) \tabularnewline
\hline
$\theta$ & 92871.84 (N/A)\tabularnewline
$\nu$ & 0.134 (0.132, 0.135)\tabularnewline
$R$ & 9370 (8950, 9780)\tabularnewline
$\delta$ & 362 (347, 377)\tabularnewline
$r/m$ & 4.66 (4.45, 4.87)\tabularnewline
$\rho/\theta$ & 0.101 (0.096, 0.105)\tabularnewline
TMRCA & 0.331 (0.324, 0.337)\tabularnewline
$T$ & 1.02 (1.01, 1.04)\tabularnewline
\hline
\end{tabular}
\label{tab:clonalframe}
\end{table}
%\clearpage{}
%=============================================================================

>>>>

%\section*{References}
% The bibtex filename
\bibliographystyle{plos}
\bibliography{siepel-strep}
\clearpage{}

@@

Figure \ref{fig:tree5}.\ {\bf The species tree of the five genomes.}
SPY is the branch of a clade of \textit{Streptococcus
pyogenes}, SDE is that for \textit{S.\ dysgalactiae} ssp.\textit{\ equisimilis},
and SD is the branch for the three individual genomes of \textit{S.\
dysgalactiae}. The scale is proportional to the expected number of mutations
given the Watterson's estimate of mutation rate and the tree.

Figure \ref{fig:Heatmap-of-recombination}.\ {\bf Heatmap of recombination events 
using the five genomes.}
Each cell of the heat map represents the logarithm base
2 of the number of recombination events inferred relative to its expectation
under the prior, for a donor and recipient pair of branches. The donor is given by
the y-axis; the recipient on the x-axis.  The black colored cells are meaningless
because the recipient species tree branch of the cells are older than the donor
species branch.

Figure \ref{fig:Gene-duplication-loss}.\ {\bf Distribution of inferred gene 
duplication, loss, and transfer events across
the phylogeny.}  Gene counts for
each extant and ancestral species are given at each node of the phylogeny.  For
each branch we denote the number of gains G*, duplications D*, losses L*,
non-recombining transfers T*, and recombinations R*.  The non-recombining
transfer and recombination counts are indicated on the recipient branch (donors
are not indicated).

Figure \ref{fig:h3}.\ {\bf Simulations of the model-based approach for assessing 
the power of recovering recombinant edges.} 
Pairs of species tree branches are shown at x-axis labels.
Three intervals are displayed for each pair. Intervals with solid line with open
circle in the middle are for the logarithm of the fraction to base 2 of the average
number of recombinant edges from the ten simulated recombinant trees 
to the numbers of recombinant edges estimated from Simulation 2. 
Interverals with dotted line are for the logarithm of the fraction to base 2 of
the number of recombinant edges estimated from the real data
to the numbers of recombinant edges estimated from Simulation 2.
Intervals with solid line with closed circle in the middle are for the logarithm
of the fraction to base 2 of the number of recombinant edges estimated from the real data
to the numbers of recombinant edges estimated from Simulation 3. 
The horizontal lines are at the zero.
The intervals range from 5\% quantile to 95\% of quantile.

@@

%=============================================================================
% Table 1. 
\begin{table}[!ht]
\caption{
\bf{Functional categories asscoiated with 
recombination intensity based on topology-altering recombinant edges.}}
\noindent \begin{centering}
\begin{tabular}{cccl}
\hline 
P-Value & Count & GO term & Description\tabularnewline
\hline 
1.731e-06 & 38 & GO:0009401 & phosphoenolpyruvate-dependent sugar phosphotransferase system\tabularnewline
2.775e-06 & 33 & GO:0008982 & protein-N(PI)-phosphohistidine-sugar phosphotransferase activity\tabularnewline
4.581e-05 & 22 & GO:0006633 & fatty acid biosynthetic process\tabularnewline
0.0001248 & 20 & GO:0008610 & lipid biosynthetic process\tabularnewline
0.0002675 & 45 & GO:0008643 & carbohydrate transport\tabularnewline
0.000513 & 81 & GO:0006412 & translation\tabularnewline
0.0005617 & 13 & GO:0006814 & sodium ion transport\tabularnewline
0.001019 & 40 & GO:0030529 & ribonucleoprotein complex\tabularnewline
0.001203 & 12 & GO:0031402 & sodium ion binding\tabularnewline
0.00206 & 39 & GO:0003735 & structural constituent of ribosome\tabularnewline
0.002115 & 237 & GO:0008152 & metabolic process\tabularnewline
0.00215 & 26 & GO:0019843 & rRNA binding\tabularnewline
0.00287 & 371 & GO:0016740 & transferase activity\tabularnewline
0.003552 & 66 & GO:0005840 & ribosome\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\label{tab:functional}
\end{table}
%\clearpage{}
%=============================================================================

%=============================================================================
% Table 2. 
\begin{table}[!ht]
\caption{
\bf{Functional categories asscoiated with 
non-recombining horizontal gene transfer.}}
\noindent \begin{centering}
\begin{tabular}{cccl}
\hline 
P-Value & Count & GO term & Description \\
\hline 
7e-61 &  67 & GO:0006313 & transposition, DNA-mediated\\
3e-58 &  59 & GO:0004803 & transposase activity\\
1e-30 &  52 & GO:0015074 & DNA integration\\
1e-28 &  23 & GO:0032196 & transposition\\
1e-13 & 527 & GO:0003677 & DNA binding\\
2e-12 &  86 & GO:0006310 & DNA recombination\\
1e-11 & 197 & GO:0003676 & nucleic acid binding\\
3e-09 &  36 & GO:0016987 & sigma factor activity\\
3e-09 &  36 & GO:0006352 & transcription initiation\\
3e-08 & 142 & GO:0043565 & sequence-specific DNA binding\\
\hline 
\end{tabular}
\par\end{centering}
\label{tab:go-events}
\end{table}
\clearpage{}
%=============================================================================

\section*{Figures}

%=============================================================================
% Figure 1: Species tree
\begin{figure}[!ht]
\includegraphics[scale=0.7]{figures/cornellf-3-tree}
\caption{
{\bf The species tree of the five genomes.} 
SPY is the branch of a clade of \textit{Streptococcus
pyogenes}, SDE is that for \textit{S.\ dysgalactiae} ssp.\textit{\ equisimilis},
and SD is the branch for the three individual genomes of \textit{S.\
dysgalactiae}. The scale is proportional to the expected number of mutations
given the Watterson's estimate of mutation rate and the tree.}
\label{fig:tree5}
\end{figure}
\clearpage{}%
%=============================================================================

%=============================================================================
% Figure 2. Heat map of recombining gene transfer from ClonalOrigin
\begin{figure}
\includegraphics[scale=0.45]{figures/heatmap-recedge}
\caption{\label{fig:Heatmap-of-recombination}
{\bf Heatmap of recombination events using the five genomes.}
Each cell of the heat map represents the logarithm base
2 of the number of recombination events inferred relative to its expectation
under the prior, for a donor and recipient pair of branches. The donor is given by
the y-axis; the recipient on the x-axis.  The black colored cells are meaningless
because the recipient species tree branch of the cells are older than the donor
species branch.}
\end{figure}
\clearpage{}
%=============================================================================

%=============================================================================
% Figure 3. Gene duplication, loss, and transfer
\begin{figure}
\includegraphics[width=6in]{figures/strep-events}
\caption{\label{fig:Gene-duplication-loss} 
{\bf Distribution of inferred gene duplication, loss, and transfer events across
the phylogeny.}  Gene counts for
each extant and ancestral species are given at each node of the phylogeny.  For
each branch we denote the number of gains G*, duplications D*, losses L*,
non-recombining transfers T*, and recombinations R*.  The non-recombining
transfer and recombination counts are indicated on the recipient branch (donors
are not indicated).}
\end{figure}
\clearpage{}%
%=============================================================================

@@

\caption{
{\bf Simulations of the model-based approach for assessing the power of recovering
recombinant edges.} Pairs of species tree branches are shown at x-axis labels.
Three intervals are displayed for each pair. Intervals with solid line with open
circle in the middle are for the logarithm of the fraction to base 2 of the average
number of recombinant edges from the ten simulated recombinant trees 
to the numbers of recombinant edges estimated from Simulation 2. 
Interverals with dotted line are for the logarithm of the fraction to base 2 of
the number of recombinant edges estimated from the real data
to the numbers of recombinant edges estimated from Simulation 2.
Intervals with solid line with closed circle in the middle are for the logarithm
of the fraction to base 2 of the number of recombinant edges estimated from the real data
to the numbers of recombinant edges estimated from Simulation 3. 
The horizontal lines are at the zero.
The intervals range from 5\% quantile to 95\% of quantile.}
\label{fig:h3}
\end{figure}
\clearpage{}%
%=============================================================================

@@

%=============================================================================
% Table S2. ClonalFrame Result.
\begin{table}[!ht]
\caption{
\bf{Parameter estimates from \texttt{ClonalFrame}.}
\noindent \centering{}\begin{tabular}{cc}
\hline
Parameter & Estimates (95\% credibility interval) \tabularnewline
\hline
$\theta^a$ & 92871.84 (N/A)\tabularnewline
$\nu^b$ & 0.134 (0.132, 0.135)\tabularnewline
$R^c$ & 9370 (8950, 9780)\tabularnewline
$\delta^d$ & 362 (347, 377)\tabularnewline
$r/m^e$ & 4.66 (4.45, 4.87)\tabularnewline
$\rho/\theta^f$ & 0.101 (0.096, 0.105)\tabularnewline
TMRCA$^g$ & 0.331 (0.324, 0.337)\tabularnewline
$T^h$ & 1.02 (1.01, 1.04)\tabularnewline
\hline
\end{tabular}
\begin{flushleft}
$^a$ $\theta$ is population mutation rate,

$^d$ $\delta$ is the average recombinant tract length,

$^e$ $r/m$ is the relative strength of recombination compared to mutations,

$^g$ TMRCA is the time to most recent common ancestor, and

$^h$ $T$ is the total branch length of the inferred species tree.}
\end{flushleft}
\label{tab:clonalframe}
\end{table}
%\clearpage{}
%=============================================================================
